Summarize twas

### 2020-07-24 analysis/index.Rmd
chr17:22

>>>>

## Summarize cTWAS results
We compare cTWAS results with other methods, summarizing results over multiple simulation runs.

  * [Using UKbiobank data (chr22), fusion weights Adipose](simulation-multi-ukbchr22-gtex.adipose.html)
  * [Using UKbiobank data (chr22), fusion weights Adipose, setting 2](simulation-multi-ukbchr22-gtex.adipose2.html)
  * [Using UKbiobank data (chr17:22), fusion weights Adipose](simulation-multi-ukbchr17:22-gtex.adipose.html)

### 2020-07-24 analysis/simulation-multi-ukbchr22-gtex.adipose.Rmd
chr17:22

Run simulation 8 times for ukb chr 17 to chr 22 combined.

```{r plot functions}
library(mr.ash.alpha)
library(data.table)
suppressMessages({library(plotly)})
library(tidyr)
library(plyr)
```
```{r output dir}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/"
outputdir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/"
susiedir <- "~/causalTWAS/simulations/simulation_susietest_20200721/"
tags <- paste0('20200721-1-', c(2,4:9))
tag2s <- c('zeroes-es', 'zerose-es', 'lassoes-es','lassoes-se')
```

@@

@@

@@

>>>>

Run simulation 9 times for ukb chr 22.

```{r plot functions}
library(mr.ash.alpha)
library(data.table)
suppressMessages({library(plotly)})
library(tidyr)
library(plyr)
```
```{r output dir}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20200616/"
outputdir <- "~/causalTWAS/simulations/simulation_ashtest_20200616/"
susiedir <- "~/causalTWAS/simulations/simulation_susietest_20200616/"
tags <- paste0('20200616-7-', 1:9)
tag2s <- c('expr-snp', 'snp-expr', 'lassoexpr-snp','lassoSNPes-es','lassoes-se' )
```

@@

## lassosnp; expr-snp; expr-snp

```{r param 5}
show_param(tag2s[5])
```

@@

## lassosnp; expr-snp; expr-snp

```{r sca 5, fig.height=4, fig.width=10}
scatter_plot_PIP(tag2s[5])
```

@@

## lassosnp; expr-snp; expr-snp

```{r roc 5, fig.height=4, fig.width=4}
ROC_plot(tag2s[5])
```

### 2020-07-24 analysis/simulation-multi-ukbchr22-gtex.adipose2.Rmd
chr17:22

```{r plot functions}
library(mr.ash.alpha)
library(data.table)
suppressMessages({library(plotly)})
library(tidyr)
library(plyr)
```
```{r output dir}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20200616/"
outputdir <- "~/causalTWAS/simulations/simulation_ashtest_20200616/"
susiedir <- "~/causalTWAS/simulations/simulation_susietest_20200616/"
tags <- paste0('20200616-7-', 1:9)
tag2s <- c('expr-snp', 'snp-expr', 'lassoexpr-snp','lassoSNPes-es','lassoes-se' )
```

@@

## lassosnp; expr-snp; expr-snp

```{r param 5}
show_param(tag2s[5])
```

@@

## lassosnp; expr-snp; expr-snp

```{r sca 5, fig.height=4, fig.width=10}
scatter_plot_PIP(tag2s[5])
```

@@

## lassosnp; expr-snp; expr-snp

```{r roc 5, fig.height=4, fig.width=4}
ROC_plot(tag2s[5])
```

>>>>

```{r plot functions}
library(mr.ash.alpha)
library(data.table)
suppressMessages({library(plotly)})
library(tidyr)
library(plyr)
```
```{r output dir}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20200616/"
outputdir <- "~/causalTWAS/simulations/simulation_ashtest_20200616/"
susiedir <- "~/causalTWAS/simulations/simulation_susietest_20200616/"
tags <- paste0('20200616-8-', 1:9)
tag2s <- c('zeroes-es', 'zerose-es', 'lassoes-es','lassoes-se')
```

@@

@@

@@
